---
title: "Comparison between old and new MSE code"
date: "Oct 13, 2020"
output: 
  pdf_document
urlcolor: blue
---

```{r setup, include = FALSE}
library(devtools)
library(gridExtra)
library(here)
library(knitr)
load_all("../../pacifichakemse")
#library(pacifichakemse)

knitr_figs_dir <- "knitr-figs-pdf/"
knitr_cache_dir <- "knitr-cache-pdf/"
fig_out_type <- "pdf"
fig_asp <- 0.618
fig_width <- 9
fig_out_width <- "6in"
fig_dpi <- 180
fig_align <- "center"
fig_pos <- "htb"
opts_chunk$set(
  fig.pos = "!H",
  out.extra = "",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = knitr_figs_dir,
  cache.path = knitr_cache_dir,
  fig.asp = fig_asp,
  fig.width = fig_width,
  out.width = fig_out_width,
  echo = FALSE,
  #  autodep = TRUE,
  #  cache = TRUE,
  cache.comments = FALSE,
  dev = fig_out_type,
  dpi = fig_dpi,
  fig.align = fig_align,
  fig.pos = fig_pos)

theme_set(hake_theme())

if(!file.exists("om_0.rds") |
   !file.exists("om_1.rds") |
   !file.exists("om_2.rds")){

  set.seed(12345)
  seed <- floor(runif(n = 1, min = 1, max = 1e6))

  ss_model_yr <- 2018
  ss_model_output_dir <- file.path(system.file(package = "pacifichakemse", mustWork = TRUE),
                                   "extdata", paste0("SS3_", ss_model_yr))
  ss_model_data_csv_dir <- file.path(system.file(package = "pacifichakemse", mustWork = TRUE),
                                     "extdata", "csv-data")
  ss_model <- load_ss_model_data(ss_model_output_dir = ss_model_output_dir,
                                 ss_model_data_csv_dir = ss_model_data_csv_dir,
                                 load_extra_mcmc = FALSE,
                                 overwrite_ss_rds = TRUE)
  
  om <- load_data_om(ss_model, yr_future = 50)

  om$selectivity_change <- 0
  om_0 <- run_om(om, random_seed = seed, verbose = FALSE)
  saveRDS(om_0, "om_0.rds")

  om$selectivity_change <- 1
  om_1 <- run_om(om, random_seed = seed, verbose = FALSE)
  saveRDS(om_1, "om_1.rds")
  
  om$selectivity_change <- 2
  om_2 <- run_om(om, random_seed = seed, verbose = FALSE)
  saveRDS(om_2, "om_2.rds")
}

om <- om_0 <- readRDS("om_0.rds")
om_1 <- readRDS("om_1.rds")
om_2 <- readRDS("om_2.rds")
```

## Comparison of OM outputs

The following plots show comparisons between the old OM code (Nis') and the new OM code (*pacifichakemse*). All the outputs shown here have associated automated tests in the *pacifichakemse* package, and all comparisons with the old code produce identical results. The choice for future recruitment seed greatly affects the projected years in both the old and new OMs, but it affects them the same way (i.e the results with any given seed are identical).

To see these tests, look in this file: https://github.com/pacific-hake/pacifichakemse/blob/master/tests/testthat/test-run-om.R

There are several part of the new OM that have hardwired values that were used in the old OM. These were temporarily added to the new code to make sure that the model outputs are the same and should be removed and the testing suite changed once we are satisfied that this is working as it should. Here is a list of Github permalinks to the lines in files that have been hardwired:

- [calc_catch_seas_country.R](https://github.com/pacific-hake/pacifichakemse/blob/ed020567e7801fde9b81bc81eba92bb0b5eb3f4d/R/calc_catch_seas_country.R#L82)
- [extract_catch_country.R](https://github.com/pacific-hake/pacifichakemse/blob/ed020567e7801fde9b81bc81eba92bb0b5eb3f4d/R/extract_catch_country.R#L32)
- [run_multiple_MSEs.R](https://github.com/pacific-hake/pacifichakemse/blob/ed020567e7801fde9b81bc81eba92bb0b5eb3f4d/R/run_multiple_MSEs.R#L101)
- [ss-model-loading.R](https://github.com/pacific-hake/pacifichakemse/blob/ed020567e7801fde9b81bc81eba92bb0b5eb3f4d/R/ss-model-loading.R#L431)

The catch-by-country data is located in the file [landings-tac-history.csv](https://github.com/pacific-hake/pacifichakemse/blob/master/inst/extdata/csv-data/landings-tac-history.csv). When the two values of catch for each year are summed, they do not add up to the total catch in the SS model data file for the years after 2005. This is an issue with the assessment as well and needs fixing. 

For the by-country catch, the new OM uses what is in the [landings-tac-history.csv](https://github.com/pacific-hake/pacifichakemse/blob/master/inst/extdata/csv-data/landings-tac-history.csv) file, but the old code uses the catch from the file [catch_per_country.csv](https://github.com/pacific-hake/pacifichakemse/blob/master/inst/extdata/csv-data/catch_per_country.csv) and the new OM has that hardwired in temporarily because the values are different in the two files. We should decide which to use and figure out how the [catch_per_country.csv](https://github.com/pacific-hake/pacifichakemse/blob/master/inst/extdata/csv-data/catch_per_country.csv) file was calculated. See the relevant code lines here: 
https://github.com/pacific-hake/pacifichakemse/blob/ed020567e7801fde9b81bc81eba92bb0b5eb3f4d/R/load_dat_om.R#L270

```{r ssb, fig.cap = "SSB difference between the two Operating models. These OMs are conditioned to 2018, and are simulated to 2023. The random seed used for both here is  Note that the lines are exactly overlapping for the whole time series."}
compare_biomass(om)
```

```{r age-comps-season-3, fig.cap = "Weighted average age in catch for the old and new OMs for season 3. This is calculated as the sum of (mean of country age proportions * age vector)."}
compare_age_comps(om)
```

```{r age-comps-season-4, fig.cap = "Weighted average age in catch for the old and new OMs for season 4."}
compare_age_comps(om, season = 4)
```

\clearpage

```{r age-in-catch-by-country, fig.cap = "Weighted average age in catch by country for the new OM. This is calculated as the mean of [(F_season / Z) * (1 - exp(-Z) * numbers-at-age * weight-at-age] * age vector"}
compare_age_in_catch(om$catch_save_age)
```

```{r age-in-catch-by-country-old, fig.cap = "Average age in catch by country for the old OM."}
fn <- file.path(system.file(package = "pacifichakemse", mustWork = TRUE),
                "extdata", "om_nis.rds")
om_nis <- readRDS(fn)
compare_age_in_catch(om_nis$Catch.save.age)
```

```{r movement, fig.cap = "Movement by season and country for the new OM"}
fn <- file.path(system.file(package = "pacifichakemse", mustWork = TRUE),
                "extdata", "om_nis.rds")
om_nis <- readRDS(fn)

p <- compare_move(om)
do.call("grid.arrange", c(p, ncol = 2))
```

```{r movement-old, fig.cap = "Movement by season and country for the old OM"}
fn <- file.path(system.file(package = "pacifichakemse", mustWork = TRUE),
                "extdata", "om_nis.rds")
om_nis <- readRDS(fn)
om_nis$ages <- om$ages
om_nis$n_age <- om$n_age
p <- compare_move(om_nis)
do.call("grid.arrange", c(p, ncol = 2))
```

\clearpage

### Comparison of different selectivity scenarios

```{r sel-by-country-new, fig.cap = "Selectivity scenarios by country for the new OM"}
plot_selectivity_scenarios(om_0, om_1, om_2)
```

```{r sel-by-country-old, fig.cap = "Selectivity scenarios by country for the old OM"}
plot_selectivity_scenarios(om_0, om_1, om_2, "old")
```
